---
title: "Basices of Quarto documentation"
author: "Usman Afzali"
date: "2022-12-22"
output: 
  html_document: 
    theme: cerulean
    highlight: espresso
    toc: yes
    number_sections: yes
---

# Heading 1

## Heading 2

### Heading 3

#### Heading 4

##### Heading 5

###### Heading 6

*Italic*

**Bold**

***Bold Italic***

1.  List item 1
2.  List item 2

-   bullet 1
-   bullet 2

Link: [My website](https://www.usmanafzali.com)

```{r}
answer <- 2 + 4
answer
my_data <- cars
my_data
```

To run each `line`, say for testing, use `command + return`.

# Including Plots

```{r}
plot(my_data$speed ~ my_data$dist)
```

You can also embed plots, for example: Here, `echo=FALSE` means that the code will not be shown.

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r include=FALSE}
library(viridis)
```

# Viridis colours

```{r}
image(volcano, col = viridis(200, option = "A"))
```

# References

1.  [Git and GitHub with RStudio On Mac - 2022](https://github.com/usman-afzali/Git-GitHub-Mac-2022)

2.  [R Markdown TUTORIAL \| A powerful tool for LEARNING R (IN 45 MINUTES)](https://youtu.be/K418swtFnik)

# Session Info:

```{r}
sessionInfo()
```
