---
title: "Assessing New Zealand Tertiary Students' Financial Stress using Students' Financial Stress Scale-Aotearoa"
author: "Usman Afzali"
date: "2023-03-11"
categories: [stats, financial stress]
---

This project was completed in 2018 for my BSc Honours degree thesis. I tried to examine New Zealand Tertiary students' financial stress with respect to free education (fees-free), debt, subjective social students, and several financial and demographic variables using `Students' Financial Stress Scale - Aotearoa`.

The Honours thesis provides a complete account of this work. A scientific paper communicating the most substantial findings has been [published](https://www.usmanafzali.com/publications/2779-perception-of-financial-satisfaction-and-its-implications-for-free-first-year-education-in-new-zealand-university-students) in New Zealand Journal of Psychology.

This document provides full data analysis of the thesis. The raw data is not available due to confidentiality and privacy reasons.

```{r}
df <- readxl::read_xlsx("S1-200-300.xlsx")
str(df)
```

```{r}
df <- df[-c(1), ]
df
```


```{r}
library(dplyr)
df <- df %>% select(`SFSS-A_1`, `SFSS-A_2`, `SFSS-A_3`, `SFSS-A_4`, `SFSS-A_5`, `SFSS-A_6`, `SFSS-A_7`, `SFSS-A_8`, `SFSS-A_9`, `SFSS-A_10`, `SFSS-A_11`, `SFSS-A_12`, `SFSS-A_13`, `SFSS-A_14`, `SFSS-A_15`, `SFSS-A_16`, `SFSS-A_17`, `SFSS-A_18`, `SFSS-A_19`, `SFSS-A_20`, `SFSS-A_21`, `SFSS-A_22`, `Scale`, `Age`, `Gender`, `Study`, `Fulltime`, `ETH`, `ETH_8_TEXT`, `EMPL`, `ALLOW`, `FIN-SUP`, `FIN-SUP_3_TEXT`, `DEBT`)
df
```


```{r}
library(tidyverse)
df <- df %>%
  mutate(`SFSS-A_1` = as.numeric(`SFSS-A_1`)) %>%
  mutate(`SFSS-A_2` = as.numeric(`SFSS-A_2`)) %>%
  mutate(`SFSS-A_3` = as.numeric(`SFSS-A_3`)) %>%
  mutate(`SFSS-A_4` = as.numeric(`SFSS-A_4`)) %>%
  mutate(`SFSS-A_5` = as.numeric(`SFSS-A_5`)) %>%
  mutate(`SFSS-A_6` = as.numeric(`SFSS-A_6`)) %>%
  mutate(`SFSS-A_7` = as.numeric(`SFSS-A_7`)) %>%
  mutate(`SFSS-A_8` = as.numeric(`SFSS-A_8`)) %>%
  mutate(`SFSS-A_9` = as.numeric(`SFSS-A_9`)) %>%
  mutate(`SFSS-A_10` = as.numeric(`SFSS-A_10`)) %>%
  mutate(`SFSS-A_11` = as.numeric(`SFSS-A_11`)) %>%
  mutate(`SFSS-A_12` = as.numeric(`SFSS-A_12`)) %>%
  mutate(`SFSS-A_13` = as.numeric(`SFSS-A_13`)) %>%
  mutate(`SFSS-A_14` = as.numeric(`SFSS-A_14`)) %>%
  mutate(`SFSS-A_15` = as.numeric(`SFSS-A_15`)) %>%
  mutate(`SFSS-A_16` = as.numeric(`SFSS-A_16`)) %>%
  mutate(`SFSS-A_17` = as.numeric(`SFSS-A_17`)) %>%
  mutate(`SFSS-A_18` = as.numeric(`SFSS-A_18`)) %>%
  mutate(`SFSS-A_19` = as.numeric(`SFSS-A_19`)) %>%
  mutate(`SFSS-A_20` = as.numeric(`SFSS-A_20`)) %>%
  mutate(`SFSS-A_21` = as.numeric(`SFSS-A_21`)) %>%
  mutate(`SFSS-A_22` = as.numeric(`SFSS-A_22`)) %>%
  mutate(`Scale` = as.numeric(`Scale`))

str(df)
```

```{r}
reverse_scores = c("SFSS-A_4", "SFSS-A_20")
df [ , reverse_scores] = 8 - df [ , reverse_scores]
```

```{r}
df$SFSS_A <- rowMeans(df[,c("SFSS-A_2", "SFSS-A_3", "SFSS-A_4", "SFSS-A_5", "SFSS-A_6", "SFSS-A_7", "SFSS-A_8", "SFSS-A_9", "SFSS-A_12", "SFSS-A_13", "SFSS-A_14", "SFSS-A_16", "SFSS-A_17", "SFSS-A_18", "SFSS-A_20", "SFSS-A_21", "SFSS-A_22")], na.rm = TRUE)
psych::describe(df$SFSS_A)
```

## TBC









